\todo{New title} Concretizing the Process Hitting into Biological Regulatory Networks

### 2013-05-03 parts/grn.tex
discussion on edge a -2 b

\paragraph{Discussion on maximum level restrictions}
The maximum level $l_a$ of a component $a$ is usually chosen equal to the number of outgoing edges of $a$ in the IG, \ie the number of components that $a$ regulates.
Indeed, each discrete expression level in $\segm{0}{l_a}$ stands for an arbitrary set of concentration levels for which $a$ has a certain influence on several other components it regulates.
Allowing more expression levels makes several levels useless as they represent the same influence of $a$ than some other levels;
on the contrary, reducing the maximum level requires that several thresholds on outgoing edges of $a$ share the same value, which is biologically unlikely.
However, these considerations are usually taken into account when one has to directly build a model in this framework, but are not mandatory.
In the scope of this paper, we allow any number of levels for components, without considering the number of outgoing edges,
as the number of processes in a PH sort is not constrained in any way.
For instance, in the example of \pref{fig:runningBRN}, it would be more relevant to have $l_a = 1$, as $a$ has only one outgoing edge;
however, the value $l_a = 2$ makes the example more interesting.

>>>>

\paragraph{Discussion on maximum level restrictions}
The maximum level $l_a$ of a component $a$ is usually chosen equal to the number of outgoing edges of $a$ in the IG, \ie the number of components that $a$ regulates.
Indeed, each discrete expression level in $\segm{0}{l_a}$ stands for an arbitrary set of concentration levels for which $a$ has a certain influence on several other components it regulates.
Allowing more expression levels makes several levels useless as they represent the same influence of $a$ than some other levels;
on the contrary, reducing the maximum level requires that several thresholds on outgoing edges of $a$ share the same value, which is biologically unlikely.
However, these considerations are usually taken into account when one has to directly build a model in this framework, but are not mandatory.
In the scope of this paper, we allow any number of levels for components, without considering the number of outgoing edges,
as the number of processes in a PH sort is not constrained in any way.
For instance, in the example of \pref{fig:runningBRN},
it would be more relevant to have $l_a = 1$ and $\GRNedgef{a}{-}{1}{b} \in E$, as $a$ has only one outgoing edge,
but the value $l_a = 2$ makes the example more interesting, therefore $\GRNedgef{a}{-}{2}{b} \in E$ can be arbitrarily chosen.
